{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-30 brains-protocol.tex
4.2 reorganized v2

We also introduce a null hypothesis $\mathcal{H}_0$ to compare the actual variation of a word's feature to its expected variation, assuming the arrival word $\warrival$ has been chosen randomly from the pool of free association words.
In this case, since $\phi(\warrival)$ becomes a constant value in the above averaging (by definition $\warrival$ does not depend on $\wstart$ anymore),  the baseline variation under $\mathcal{H}_0$ may be rewritten as:
$$\nu_{\phi}^0 (f) = \left<\phi\right>$$
We thereby obtain the mean variation of feature for each start feature value, comparing the variations to a situation where arrival words are chosen randomly.\footnote{We additionally considered an alternative null hypothesis, denoted $\mathcal{H}_{00}$, where the arrival word is randomly chosen \emph{among immediate synonyms of the start word}, \hbox{i.e.} an arrival word chosen among semantically plausible though still random words. In this case $\warrival_{00}$ does depend on $\wstart$. The results were not qualitatively different under this second null hypothesis, so for the sake of clarity we chose to keep the simpler~$\mathcal{H}_0$.}

\medskip
On the whole, this method gives us a fine-grained view of how word features evolve upon substitution with respect to (i) the original feature (\hbox{vs.} $y=x$) and (ii) a random arrival (\hbox{vs.} $\mathcal{H}_0$).
Results are gathered on Fig.~\ref{fig:feature-variations}.

We can do a first striking observation: all graphs show the existence of a unique intersection of $\nu_{\phi}$ with $y=x$, while the slope of $\nu_{\phi}$ is smaller than 1.  In other words, there exists a unique attractor for all features.  
Second, the comparison with $\mathcal{H}_0$ shows that we have two classes of attractors, depending on whether (i) there is a triple intersection (of $y=x$, $\mathcal{H}_0$ and $\nu_{\phi}$) or (ii) $\mathcal{H}_0$ remains always above or below $\nu_{\phi}$.

>>>>

We also introduce a null hypothesis $\mathcal{H}_0$ to compare the actual variation of a word's feature to its expected variation, assuming the arrival word $\warrival$ has been chosen randomly from the pool of free association words.
In this case, since $\phi(\warrival)$ becomes a constant value in the above averaging (by definition $\warrival$ does not depend on $\wstart$ anymore),  the baseline variation under $\mathcal{H}_0$ may be rewritten as:\footnote{We additionally considered an alternative null hypothesis, denoted $\mathcal{H}_{00}$, where the arrival word is randomly chosen \emph{among immediate synonyms of the start word}, \hbox{i.e.} an arrival word chosen among semantically plausible though still random words. In this case $\warrival_{00}$ does depend on $\wstart$. The results were not qualitatively different under this second null hypothesis, so for the sake of clarity we chose to keep the simpler~$\mathcal{H}_0$.}
$$\nu_{\phi}^0 (f) = \left<\phi\right>$$
%We thereby obtain the mean variation of feature for each start feature value, comparing the variations to a situation where arrival words are chosen randomly.

This approach yields a fine-grained view of how word features evolve upon substitution, on average, with respect to (i) the original feature (\hbox{vs.} $y=x$) and (ii) a random arrival (\hbox{vs.} $\mathcal{H}_0$).

\medskip Results are gathered on Fig.~\ref{fig:feature-variations}.
 We can do a first striking observation: all graphs show the existence of a unique intersection of $\nu_{\phi}$ with $y=x$, while the slope of $\nu_{\phi}$ is smaller than 1.  In other words, there exists a unique attractor for all features.  
Second, the comparison with $\mathcal{H}_0$ shows that we have two classes of attractors, depending on whether (i) there is a triple intersection (of $y=x$, $\nu_{\phi}^0$ and $\nu_{\phi}$) or (ii) $\nu_{\phi}$ remains always above or below $\nu_{\phi}^0$.
